State of the Practice for Medical Imaging Software

### 2022-09-30 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Updates to MI SOP paper

We aim to study the state of software development practice for Medical Imaging
(MI) software.  MI tools use images of the interior of the body (from sources
such as Magnetic Resonance Imaging (MRI), Computed Tomography (CT), Positron
Emission Tomography (PET) and Ultrasound) to provide information for diagnostic,
analytic, and medical applications \citep{FDA2021, enwiki:1034887445,
Zhang2008}.  An example medical image of the brain is provided in
Figure~\ref{Fig_Example}. Given the importance of MI software and the high
number of competing software projects, we wish to understand the merits and
drawbacks of the current development processes, tools and methodologies.  We aim
to assess through a software engineering lens the quality of the existing
software with the hope of highlighting standout examples, understanding current
pain points and providing guidelines and recommendations for future development.

@@

To gain insights, we devised 10 research questions, which can be applied to MI,
as well as to other domains, of research software \citep{SmithEtAl2021,
SmithAndMichalski2022}.  The questions are designed to learn about the
community's interest in, and experience with, artifacts, tools, principles,
processes, methodologies and qualities.  When we mention artifacts we mean the
documents, scripts and code that constitutes a software development project.
Example artifacts include requirements, specifications, user manuals, unit
tests, system tests, usability tests, build scripts, API (Application
Programming Interface) documentation, READMEs, license documents, process
documents, and code.  Once we have learned what MI developers do, we then put
this information in context by contrasting MI software against the trends shown
by developers in other research software communities.  Our aim is to collect
enough information to understand the current pain points experienced by the MI
software development community so that we can make some preliminary
recommendations for future improvements.

The questions are used to structure the discussion in the paper, so for each
research question below we point to the section that contains our answer.  We
start with identifying the relevant examples of MI software:

\begin{enumerate}
	\item[RQ\refstepcounter{rqnum}\therqnum \label{RQ_WhatProjects}:] What MI
	software projects exist, with the constraint that the source code must be
	available for all identified projects? (Section~\ref{ch_results})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_HighestQuality}:] Which
	of the projects identified in \rqref{RQ_WhatProjects} follow current best
	practices, based on evidence found by experimenting with the software and
	searching the artifacts available in each project's repository?
	(Section~\ref{ch_results})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareHQ2Popular}:] How
	similar is the list of top projects identified in \rqref{RQ_HighestQuality}
	to the most popular projects, as viewed by the scientific community?
	(Section~\ref{Sec_VsCommunityRanking})
    \item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareArtifacts}:] How
	do MI projects compare to research software in general with respect to the
	artifacts present in their repositories?
	(Section~\ref{Sec_CompareArtifacts})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareToolsProjMngmnt}:]
	How do MI projects compare to research software in general with respect to
	the use of tools (Section~\ref{Sec_CompareTools}) for:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareToolsProjMngmnt}.a] development; and,
		\item [\rqref{RQ_CompareToolsProjMngmnt}.b] project management?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareMethodologies}:]
	How do MI projects compare to research software in general with respect to
	principles, processes and methodologies used?
	(Section~\ref{Sec_CompareMethodologies})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_PainPoints}:] What are
	the pain points for developers working on MI software projects?
	(Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_ComparePainPoints}:] How
	do the pain points of developers from MI compare to the pain points
	for research software in general? (Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Concerns}:] For MI
	developers what specific best practices are taken to address the pain points
	and software quality concerns? (Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Recommend}:]
	What research software development practice could potentially address the
	pain point concerns identified in \rqref{RQ_PainPoints}).
	(Section~\ref{ch_recommendations})

@@

We designed a general methodology to assess the state of the practice for SC
software \citep{SmithEtAl2021, SmithAndMichalski2022}. Details can be found in
Section~\ref{ch_methods}.  Our methodology has been applied to MI software
\citep{Dong2021} and Lattice Boltzmann Solvers \citep{Michalski2021}.  This
methodology builds off prior work to assess the state of the practice for such
domains as Geographic Information Systems \citep{smith2018state}, Mesh
Generators \citep{smith2016state}, Seismology software
\citep{Smith2018Seismology}, and Statistical software for psychology
\citep{smith2018statistical}.  In keeping with the previous methodology, we have
maintained the constraint that the work load for measuring a given domain should
be feasible for a team as small as one person, and for a short time, ideally
around a person month of effort. A person month is considered to be $20$ working
days ($4$ weeks in a month, with $5$ days of work per week) at $8$ person hours
per day, or $20 \times 8 = 160$ person hours.

@@

To measure the existing MI software we need two sets of definitions: i) the
definitions of relevant software license models (Section
\ref{sec_software_categories}); and, ii) the definitions of the software
qualities that we will be assessing (Section \ref{sec_software_quality}). In our
assessment we rank the software packages for each quality; therefore, this
section also provides the background on our ranking process -- the Analytic
Hierarchy Process (Section \ref{sec_AHP}).

@@

When assessing software packages, we need to know what license the software is
distributed under.  In particular, we need to know whether the source code will
be available to us or not.  We define three common software categories.  We will
only assess software that fits under the Open Source Software license.

@@

\item \textbf{Commercial Software} ``Commercial software is software developed
by a business as part of its business'' \citep{GNU2019}. Typically speaking, the
users are required to pay to access all of the features of commercial software,
excluding access to the source code. However, some commercial software is also
free of charge \citep{GNU2019}. Based on our experience, most commercial
software products are not OSS.

@@

Quality is defined as a measure of the excellence or worth of an entity.  As is
common practice, we do not think of quality as a single measure, but rather as a
set of measures.  That is, quality is a collection of different qualities, often
called ``ilities.''  Below we list the 10 qualities of interest for this study.
The order of the qualities follows the order used in \citet{GhezziEtAl2003},
which puts related qualities (like correctness and reliability) together.
Moreover, the order is roughly the same as the order qualities are considered in
practice.

@@

	\item \textbf{Robustness} Software possesses the characteristic of
	robustness if it behaves ``reasonably'' in two situations: i) when it
	encounters circumstances not anticipated in the requirements specification,
	and ii) when the assumptions in its requirements specification are violated
	\citep[p.\ 19]{GhezziEtAl2003}, \citep{boehm2007software}.

@@

	\item \textbf{Visibility/Transparency} The extent to which all of the steps
	of a software development process and the current status of it are conveyed
	clearly \citep[p.\ 32]{GhezziEtAl2003}.

@@

In this project, the first nine software qualities mentioned in Section
\ref{sec_software_quality} are the criteria ($m = 9$), while 29 software
packages ($n = 29$) are compared for each of the $m$ criteria. The packages are
evaluated with the grading template in Section~\ref{sec_grading_software}, which
includes a subjective score from $1$ to $10$ for each quality for each package.
For each quality, for a pair of packages $i$ and $j$, with $\mathit{score}_i >=
\mathit{score}_j$, the difference between the two scores is $\mathit{diff_{ij}}
= \mathit{score}_i - \mathit{score}_j$. The mapping between $\mathit{diff_{ij}}$
(which can vary between 0 and 9) and the values in $A_{ij}$ (which can vary
between 1 and 9) is as follows:

@@

The measurement results summarize to this point are based on information we
collect from on-line resources. This information is incomplete because it
doesn't generally capture the development process, the developer pain points,
the perceived threats to software quality, and the developers' strategies to
address these threats.  Therefore, part of our methodology is to interview
developers.

@@

Our interviews identify pain points that relate to lack of time and funding,
technology hurdles, improving correctness, and improving usability.  In this
section, we go through each pain point and contrast the MI experience with
observations from other domains.  We also cover potential ways to address the
pain points, as promoted by the community.  (Later, in
Section~\ref{ch_recommendations}, we propose additional pain mitigation
strategies based on our experience.)  In addition to pain points, we summarize
MI developer strategies for improving maintainability and reproducibility.
Although these two qualities were not explicitly idenfied as pain points, they
were discussed during our interviews.  The interviewee's practices for
addressing pain points and improving quality can potentially be emulated by
other MI developers. Moreover, these practices may provide examples that can be
followed by other research software domains.

[CHECK  THESE, after writing all the PPs] \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers :
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) [Actually mentioned by MI software],
reproducibility, and software scope determination. Although LBM developers did
not mention these pain points, we cannot conclude that they are not relevant for
LBM software development, since we only interviewed four LBM developers for
about an hour each.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} Many interviewees thought lack of time and lack of funding
(discussed next) were their most significant obstacles. Other domains of
research software also experience the lack of time pain point
\citep{PintoEtAl2018, PintoEtAl2016, WieseEtAl2019}. Our study of LBM software
\citep{SmithEtAl2022} also highlighted lack of time as a significant pain point.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} As mentioned above, developers felt the pain of having to attract
funding to develop and maintain their software. For instance, the interviewees
from \textit{3D Slicer} and \textit{OHIF} said getting funding for software
maintenance is more challenging than for funding for research. The interviewee
from the \textit{ITK-SNAP} team thought more fundings was a way to solve the
lack of time problem, because they could hire more dedicated developers. On the
other hand, the interviewee from the \textit{Weasis} team did not feel that
fundings could solve the same problem, since he still would need time to
supervise the project.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_TechnologyHurdles}:]
\textbf{Technology Hurdles:} The technology hurdles mentioned by MI develoers
include: hard to keep up with changes in OS and libraries, difficult to transer
to new technologies, hard to support multiple OS, and hard to support lower-end
computers. Developers expressed difficulty balancing between four factors:
cross-platform compatibility, convenience to development and maintenance,
performance, and security.

@@

\begin{itemize}
\item Adopting a web-based approach with backend servers, to better support
lower-end computers;
\item Using memory-mapped files to consume less computer memory, to better
support lower-end computers, 
\item Using computing power from the computers GPU for web applications;
\item Increasing funding;
\item Maintaining better documentations to ease the development and maintenance
processes;
\item Improving performance via more powerful computers, which one interviewee
pointed out has already happened to reduce the balance problem.
\end{itemize}

As the above list shows, developers perceive web-based applications to help the
balance problem.  Table~\ref{tab_native_vs_web} shows the teams' choices between
native application and web application. In all the 29 teams on our list, most
chose to develop native applications. For the eight teams we interviewed, three
of them were building web applications, and the \textit{MRIcroGL} team was
considering web-based solutions.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_Correctness}:]
\textbf{Ensuring Correctness:} Several developers noted difficulties with
ensuring correctness.

Other research software domains point to the following problems with testing: i)
\citet{PintoEtAl2018} mention the problem of insufficient testing; ii)
\citet{HannayEtAl2009} show that more developers think testing is important than
the number that believe they have a sufficient understanding of testing
concepts; and, iii) \citet{HannayEtAl2009, KanewalaAndBieman2013, KellyEtAl2011,
WieseEtAl2019} point to the oracle problem, which occurs in research software
when we do not have a means to judge the correctness of the calculated
solutions. LBM developers also found difficult with testing including difficulty
with testing the correctness of large numbers of features, and challenges with
automated testing, since free testing services do not offer adequate facilities
for large amounts of data.

@@

%\citet{WieseEtAl2019} mention data handling concerns (like data quality, data management and data privacy)

For the pain point category of testing developers identified the lack of access
to real-world datasets.  One pain point in the development process is the lack
of access to real-world datasets for testing. One threat to correctness is: with
huge datasets for testing, the tests are expensive and time-consuming. Three
interviewees endorsed self tests / automated tests, which may save time for
testing. Some proposed and proven solutions are as follows:

No interviewee provided a perfect solution to the testing problem. However,
increased connections between the development team and medical
professionals/institutions could ease the pain.

The interviewees identified multiple threats to correctness.  The most
frequently mentioned threat was complexity.  Complexity enters the software by
various means, including a variety of data formats, complicated data standards,
differing outputs between medical imaging machines, and the addition of
(non-viewing related) functionality.  Other threats to correctness identified by
at least one time include the following:
\begin{itemize}
\item Lack of real world image data for testing;
\item The team cannot use private data for debugging even when the data causes
problems; \wss{Why not?  Should ask Ao} \ad{For example, when a physician faces
some problems to use the software to display a medical image, he/she might reach
to the team for help. However, the image is private, so the physician can only
describe the problems, but not share the image with the team to reproduce the
problems for debugging.}
\item Expense and time consumed by tests because of the huge datasets;
\item Difficulty managing releases;
\item No unit tests; and,
\item No dedicated quality assurance team.
\end{itemize}

Testing was the most often mentioned strategy for ensuring correctness.  Seven
teams mentioned test related activities, including test-driven development,
component tests, integration tests, smoke tests, regression tests, self tests
and automated tests.  Another approach frequently adopted (mentioned by 3
interviewees) is a two state development process with stable releases and
nightly builds.  Other strategies for ensuring correctness that came up during
the interviews include CI/CD, using de-identified copies of medical images for
debugging, sending beta versions to medical workers who can access the data to
do the tests, and collecting/maintaining a dataset of problematic images.

>>>>

We aim to study the state of software development practice for Medical Imaging
(MI) software.  MI tools use images of the interior of the body (from sources
such as Magnetic Resonance Imaging (MRI), Computed Tomography (CT), Positron
Emission Tomography (PET) and Ultrasound) to provide information for diagnostic,
analytic, and medical applications \citep{FDA2021, enwiki:1034887445,
Zhang2008}.  Figure~\ref{Fig_Example} shows an example image of the brain. Given
the importance of MI software and the high number of competing software
projects, we wish to understand the merits and drawbacks of the current
development processes, tools, and methodologies.  We aim to assess through a
software engineering lens the quality of the existing software with the hope of
highlighting standout examples, understanding current pain points and providing
guidelines and recommendations for future development.

@@

To gain insights, we devised 10 research questions, which can be applied to MI,
as well as to other domains, of research software \citep{SmithEtAl2021,
SmithAndMichalski2022}.  We designed the questions to learn about the
community's interest in, and experience with, artifacts, tools, principles,
processes, methodologies, and qualities.  When we mention artifacts we mean the
documents, scripts and code that constitutes a software development project.
Example artifacts include requirements, specifications, user manuals, unit
tests, system tests, usability tests, build scripts, API (Application
Programming Interface) documentation, READMEs, license documents, process
documents, and code.  Once we have learned what MI developers do, we then put
this information in context by contrasting MI software against the trends shown
by developers in other research software communities.  Our aim is to collect
enough information to understand the current pain points experienced by the MI
software development community so that we can make some preliminary
recommendations for future improvements.

We based the structure of the paper on the research questions, so for each
research question below we point to the section that contains our answer.  We
start with identifying the relevant examples of MI software:

\begin{enumerate}
	\item[RQ\refstepcounter{rqnum}\therqnum \label{RQ_WhatProjects}:] What MI
	software projects exist, with the constraint that the source code must be
	available for all identified projects? (Section~\ref{ch_results})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_HighestQuality}:] Which
	of the projects identified in \rqref{RQ_WhatProjects} follow current best
	practices, based on evidence found by experimenting with the software and
	searching the artifacts available in each project's repository?
	(Section~\ref{ch_results})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareHQ2Popular}:] How
	similar is the list of top projects identified in \rqref{RQ_HighestQuality}
	to the most popular projects, as viewed by the scientific community?
	(Section~\ref{Sec_VsCommunityRanking})
    \item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareArtifacts}:] How
	do MI projects compare to research software in general with respect to the
	artifacts present in their repositories?
	(Section~\ref{Sec_CompareArtifacts})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareToolsProjMngmnt}:]
	How do MI projects compare to research software in general with respect to
	the use of tools (Section~\ref{Sec_CompareTools}) for:
	\begin{enumerate} 
		\item [\rqref{RQ_CompareToolsProjMngmnt}.a] development; and,
		\item [\rqref{RQ_CompareToolsProjMngmnt}.b] project management?
	\end{enumerate}
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_CompareMethodologies}:]
	How do MI projects compare to research software in general with respect to
	principles, processes, and methodologies used?
	(Section~\ref{Sec_CompareMethodologies})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_PainPoints}:] What are
	the pain points for developers working on MI software projects?
	(Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_ComparePainPoints}:] How
	do the pain points of developers from MI compare to the pain points
	for research software in general? (Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Concerns}:] For MI
	developers what specific best practices are taken to address the pain points
	and software quality concerns? (Section~\ref{painpoints})
	\item [RQ\refstepcounter{rqnum}\therqnum \label{RQ_Recommend}:]
	What research software development practice could potentially address the
	pain point concerns identified in \rqref{RQ_PainPoints}).
	(Section~\ref{ch_recommendations})

@@

We designed a general methodology to assess the state of the practice for SC
software \citep{SmithEtAl2021, SmithAndMichalski2022}. Details can be found in
Section~\ref{ch_methods}.  Our methodology has been applied to MI software
\citep{Dong2021} and Lattice Boltzmann Solvers \citep{Michalski2021}.  This
methodology builds off prior work to assess the state of the practice for such
domains as Geographic Information Systems \citep{smith2018state}, Mesh
Generators \citep{smith2016state}, Seismology software
\citep{Smith2018Seismology}, and Statistical software for psychology
\citep{smith2018statistical}.  In keeping with the previous methodology, we have
maintained the constraint that the work load for measuring a given domain should
be feasible for a team as small as one person, and for a short time, ideally
around a person month of effort. We consider a person month as $20$ working
days ($4$ weeks in a month, with $5$ days of work per week) at $8$ person hours
per day, or $20 \times 8 = 160$ person hours.

@@

To measure the existing MI software we need two sets of definitions: i) the
definitions of relevant software license models (Section
\ref{sec_software_categories}); and, ii) the definitions of the software
qualities that we will be assessing (Section \ref{sec_software_quality}). In our
assessment we rank the software packages for each quality; therefore, this
section also provides the background on our ranking process --- the Analytic
Hierarchy Process (Section \ref{sec_AHP}).

@@

When assessing software packages, we need to know the software's license.  In
particular, we need to know whether the source code will be available to us or
not.  We define three common software categories.  We will only assess software
that fits under the Open Source Software license.

@@

\item \textbf{Commercial Software} ``Commercial software is software developed
by a business as part of its business'' \citep{GNU2019}. Typically speaking, commercial software requires users to pay to access all of its features,
excluding access to the source code. However, some commercial software is also
free of charge \citep{GNU2019}. Based on our experience, most commercial
software products are not OSS.

@@

Quality is defined as a measure of the excellence or worth of an entity.  As is
common practice, we do not think of quality as a single measure, but rather as a
set of measures.  That is, quality is a collection of different qualities, often
called ``ilities.''  Below we list the 10 qualities of interest for this study.
The order of the qualities follows the order used in \citet{GhezziEtAl2003},
which puts related qualities (like correctness and reliability) together.
Moreover, the order is roughly the same as the order developers consider
qualities in practice.

@@

	\item \textbf{Robustness} Software possesses the characteristic of
	robustness if it behaves ``reasonably'' in two situations: i) when it
	encounters circumstances not anticipated in the requirements specification,
	and ii) when users violate the assumptions in its requirements specification 
	\citep[p.\ 19]{GhezziEtAl2003}, \citep{boehm2007software}.

@@

	\item \textbf{Visibility/Transparency} The extent to which all the steps
	of a software development process and the current status of it are conveyed
	clearly \citep[p.\ 32]{GhezziEtAl2003}.

@@

In this project, the first nine software qualities mentioned in Section
\ref{sec_software_quality} are the criteria ($m = 9$), while 29 software
packages ($n = 29$) are compared for each of the $m$ criteria.
Section~\ref{sec_grading_software} shows the evaluation via the grading
template, including a subjective score from $1$ to $10$ for each quality for
each package. For each quality, for a pair of packages $i$ and $j$, with
$\mathit{score}_i >= \mathit{score}_j$, the difference between the two scores is
$\mathit{diff_{ij}} = \mathit{score}_i - \mathit{score}_j$. The mapping between
$\mathit{diff_{ij}}$ (which can vary between 0 and 9) and the values in $A_{ij}$
(which can vary between 1 and 9) is as follows:

@@

The repository-based measurements summarize the information we can collect from
on-line resources. This information is incomplete because it doesn't generally
capture the development process, the developer pain points, the perceived
threats to software quality, and the developers' strategies to address these
threats.  Therefore, part of our methodology is to also interview developers.

@@

Our interviews identified pain points related to lack of time and funding,
technology hurdles, improving correctness, and improving usability.  In this
section, we go through each pain point and contrast the MI experience with
observations from other domains.  We also cover potential ways to address the
pain points, as promoted by the community.  (Later, in
Section~\ref{ch_recommendations}, we propose additional pain mitigation
strategies based on our experience.)  In addition to pain points, we summarize
MI developer strategies for improving maintainability and reproducibility.
Although these two qualities were not explicitly idenfied as pain points, they
were discussed as part of our interview process \citep{SmithEtAl2021}.  The
interviewee's practices for addressing pain points and improving quality can
potentially be emulated by other MI developers. Moreover, these practices may
provide examples that can be followed by other research software domains.

[CHECK  THESE, after writing all the PPs] \citet{PintoEtAl2018} lists some pain
points that did not come up in our conversations with MI developers :
Cross-platform compatibility, interruptions while coding, scope bloat, lack of
user feedback, hard to collaborate on software projects, and aloneness.
\citet{WieseEtAl2019} repeat some previous pain points and add the following:
dependency management, data handling concerns (like data quality, data
management and data privacy) [Actually mentioned by MI software],
reproducibility, and software scope determination. Although MI developers did
not mention these pain points, we cannot conclude that they are not relevant for
MI software development, since we only interviewed nine MI developers for about
an hour each.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} Many interviewees thought lack of time, along with lack of
funding (discussed next), were their most significant obstacles. Other domains
of research software also experience the lack of time pain point
\citep{PintoEtAl2018, PintoEtAl2016, WieseEtAl2019}. Our study of LBM software
\citep{SmithEtAl2022} also highlighted lack of time as a significant pain point.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} Developers felt the pain of having to attract funding to develop and
maintain their software. For instance, the interviewees from \textit{3D Slicer}
and \textit{OHIF} said getting funding for software maintenance is more
challenging than finding funding for research. The interviewee from the
\textit{ITK-SNAP} team thought more fundings was a way to solve the lack of time
problem, because they could hire more dedicated developers. On the other hand,
the interviewee from the \textit{Weasis} team did not feel that fundings could
solve the same problem, since he would still need time to supervise the project.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_TechnologyHurdles}:]
\textbf{Technology Hurdles:} The technology hurdles mentioned by MI developers
include: hard to keep up with changes in OS and libraries, difficult to transfer
to new technologies, hard to support multiple OS, and hard to support lower-end
computers. Developers expressed difficulty balancing between four factors:
cross-platform compatibility, convenience to development and maintenance,
performance, and security.

@@

\begin{itemize}
\item Adopting a web-based approach with backend servers, to better support
lower-end computers;
\item Using memory-mapped files to consume less computer memory, to better
support lower-end computers; 
\item Using computing power from the computers GPU for web applications;
\item Increasing funding;
\item Maintaining better documentations to ease the development and maintenance
processes;
\item Improving performance via more powerful computers, which one interviewee
pointed out has already happened to reduce the balance problem.
\end{itemize}

As the above list shows, developers perceive that web-based applications will
address the technology hurdle.  Table~\ref{tab_native_vs_web} shows the teams'
choices between native application and web application. Most of the 29 teams (24
of 29, or 83\%) chose to develop native applications. For the eight teams we
interviewed, three of them were building web applications, and the
\textit{MRIcroGL} team was considering web-based solutions.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_Correctness}:]
\textbf{Ensuring Correctness:} Interviewees identified multiple threats to
correctness.  The most frequently mentioned threat was complexity.  Complexity
enters the software by various means, including the large variety of data formats,
complicated data standards, differing outputs between medical imaging machines,
and the addition of (non-viewing related) functionality.  Other threats to
correctness identified include the following:

\begin{itemize}
\item Lack of real world image data for testing, in part because of patient
privacy concerns;
\item Tests are expensive and time-consuming because of the need for huge datasets;
\item Software releases are difficult to manage;
\item No systematic unit testing; and,
\item No dedicated quality assurance team.
\end{itemize}

**start editing here** Change to others have trouble getting developers to test.
That isn't the problem for MI.  Testing is also a pain point for other research
software domains point. For instance, \citet{PintoEtAl2018} mention the problem
of insufficient testing and \citet{HannayEtAl2009} show that more developers
think testing is important than the number that believe they have a sufficient
understanding of testing concepts. \citet{WieseEtAl2019} mention data handling
concerns (like data quality, data management and data privacy).
\citet{HannayEtAl2009, KanewalaAndBieman2013, KellyEtAl2011, WieseEtAl2019}
point to the oracle problem, which occurs in research software when we do not
have a means to judge the correctness of the calculated solutions. For the
specific case of LBM developers, testing challenges include difficulty with
testing the correctness of large numbers of features, and challenges with
automated testing, since free testing services do not offer adequate facilities
for large amounts of data \citep{SmithEtAl2022}.

Testing was the most often mentioned strategy for MI developers for ensuring
correctness.  Seven teams mentioned test related activities, including
test-driven development, component tests, integration tests, smoke tests,
regression tests, self tests and automated tests.  Another approach frequently
adopted (mentioned by 3 interviewees) is a two state development process with
stable releases and nightly builds.  Other strategies for ensuring correctness
that came up during the interviews include CI/CD, using de-identified copies of
medical images for debugging, sending beta versions to medical workers who can
access the data to do the tests, and collecting/maintaining a dataset of
problematic images.  Some additional strategies used by MI developers include:

The feedback from the interviewees makes it clear that increased connections
between the development team and medical professionals/institutions could ease
the pain of ensuring correctness via testing.

@@
